Frozen Civil Conflicts

### 2024-01-29 paper.qmd
Aggregate all the robustness checks

```{R eval = F}
models <- list.dirs("posteriors", recursive = F)
stopifnot(length(models) != 0)

@@

ll <- lapply(fits, function(fit) {
    fit$summary("ame[2,2]", pzero, quantile2, median)
}) |> bind_rows()

ggplot(ll, aes(pzero, median)) +
    geom_point() +
    geom_errorbar(aes(ymin = q5, ymax = q95))

@@

```{R eval = F}
#| fig-height: 7
summary.df <- lapply(fits, function(fit) {
    post <- post_summarise(fit, "delta", rename = T, model_info = T,
                           probs = c(0.025, 0.17, 0.5, 0.83, 0.975)) |>
        rename(median = `50%`,
               lower95 = `2.5%`,
               upper95 = `97.5%`,
               lower66 = `17%`,
               upper66 = `83%`)
}) |> bind_rows()

summary.df$variable <- sub("_(prop|bin.*)$", "", summary.df$variable)

ggplot(summary.df, aes(treatment_aggregation, median, color = outcome)) +
    geom_point(size = 1.5, position = position_dodge(width = 0.25)) +
    geom_errorbar(aes(ymin = lower95, ymax = upper95), position = position_dodge(0.25), width = 0) +
    geom_errorbar(aes(ymin = lower66, ymax = upper66), position = position_dodge(0.25), linewidth = 1.25, width = 0) +
    geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.2) +
    facet_grid(variable ~ episodes)

```{R eval = F}
regtable <- function(fits, ...) {
    names(fits) <- NULL
    modelsummary(fits, pars = c("delta", "beta", "alpha"), statistic = "conf.int", ...)
}

m <- c("frozen-bin-all", "strict_frozen-bin-all",
       "frozen-bin-high_intensity", "strict_frozen-bin-high_intensity")
regtable(fits[m], title = "Binary Treatments")
```

```{R eval = F}
m <- c("frozen-bin_5y-all", "strict_frozen-bin_5y-all",
       "frozen-bin_5y-high_intensity", "strict_frozen-bin_5y-high_intensity")
regtable(fits[m], title = "Binary Treatments - Last 5 Years")
```

```{R  eval = F}
m <- c("frozen-prop-all", "strict_frozen-prop-all",
       "frozen-prop-high_intensity", "strict_frozen-prop-high_intensity")
regtable(fits[m], title = "Proportion Treatments")
```

>>>>

```{R}
pzero <- function(x) mean(x > 0)

models <- list.dirs("posteriors", recursive = F)
stopifnot(length(models) != 0)

@@

model_ames <- lapply(fits, function(fit) {
    fit$summary("ame", pzero, posterior::quantile2, median)
}) |> bind_rows()

ll <- extract_digits(model_ames$variable)
ame_keys <- sprintf("ame[%s]", sapply(ll, `[`, 1))

model_ames$variable <- case_when(ame_keys == "ame[1]" ~ "Ext. Sup. Gov Only",
                                 ame_keys == "ame[2]" ~ "Ext. Sup. Rebel Only",
                                 ame_keys == "ame[3]" ~ "Ext. Sup. to Both")
model_ames$group <- ifelse(sapply(ll, `[`, 2) == 1, "Government Incompatibility",
                           "Territorial Incompatibility")

ggplot(model_ames, aes(pzero, median)) +
    geom_point(alpha = 0.2) +
    geom_errorbar(aes(ymin = q5, ymax = q95), alpha = 0.25) +
    geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.2) +
    facet_grid(variable ~ group) +
    labs(y = parse(text = "tilde(Delta)"), x = parse(text = "P(tilde(Delta) > 0)")) +
    theme(legend.position = "none")

@@
